Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-11-11 docs/Truman/LocalConservation/paper/paper.tex
Commented out irrelevant local conservation problems

\subsubsection{Skewed Convection-Diffusion Problem}
This is a standard convection-diffusion problem with a skewed convection
vector relative to the mesh. We take $\bbeta=(2,1)$, and on the left and
bottom inflow boundaries we impose $\hat t=1-x-y$ while the right and top
boundaries have $\hat u=0$. We solve for $\epsilon=10^{-4}$.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/modified8nc.png}
\includegraphics[width=\textwidth]{figs/Confusion/modified8nc_mesh.png}
\caption{Nonconservative}
\label{fig:confusionModified8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/modified8c.png}
\includegraphics[width=\textwidth]{figs/Confusion/modified8c_mesh.png}
\caption{Conservative}
\label{fig:confusionModified8c}
\end{subfigure}
\caption{Skewed convection-diffusion problem after 8 refinements}
\label{fig:confusion}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{figs/Confusion/modifiedFlux.pdf}
\caption{Flux imbalance in skewed convection-diffusion solutions}
\label{fig:confusionFlux}
\end{figure}

\subsubsection{Double Glazing Problem}
This nominal problem definition takes the same unit square domain with
\[
\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad
\hat u=
\begin{cases}
1 & \mbox{on }\Gamma_{right}\\
0 & \mbox{else }
\end{cases}\,,
\]
except that this definition for the boundary is not legal for $\hat u\in
H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The
results are for $\epsilon=10^{-2}$.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5nc.png}
\caption{Nonconservative}
\label{fig:doubleglazingGraph6c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5c.png}
\caption{Conservative}
\label{fig:doubleglazingRobust6c}
\end{subfigure}
\caption{Double glazing problem after 5 refinements}
\label{fig:doubleglazing}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/DoubleGlazing/modifiedFlux.pdf}
\caption{Flux imbalance in double glazing problem}
\label{fig:doubleglazingFlux}
\end{figure}

@@

\subsubsection{Wedge Problem}
We devised this problem to examine some of the issues we were having blow up
of the solution under the robust test norm. The domain is a rectangle
$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
of the wedge.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/modified16nc.png}
\includegraphics[width=\textwidth]{figs/Wedge/modified16nc_mesh.png}
\caption{Nonconservative}
\label{fig:wedgeGraph16nc}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/modified16c.png}
\includegraphics[width=\textwidth]{figs/Wedge/modified16c_mesh.png}
\caption{Conservative}
\label{fig:wedgeRobust16nc}
\end{subfigure}
\caption{Wedge problem after 16 refinements}
\label{fig:wedge}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{figs/Wedge/modifiedFlux.pdf}
\caption{Flux imbalance in wedge solutions}
\label{fig:wedge_flux}
\end{figure}

\subsubsection{Inner Layer Problem}
In this problem, $\bbeta=(\frac{\sqrt{3}}{2},\frac{1}{2})^T$ and we have a
discontinuous flux inflow condition where $\hat t=0$ if $y\le0.2$ and $\hat
t=\bbeta\cdot\mathbf{n}$ if $y>0.2$. On the outflow, $\hat u=0$. We use a very
small diffusion scale of $\epsilon=10^{-6}$ which creates a very thin inner
layer.
% Nonconservative solution in range $[-0.38, 1.34]$.
% Conservative solution in range $[-0.39, 1.38]$.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc.png}
\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc_mesh.png}
\caption{Nonconservative}
\label{fig:innerlayer8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c.png}
\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c_mesh.png}
\caption{Conservative}
\label{fig:innerlayer8c}
\end{subfigure}
\caption{Inner layer problem after 8 refinements}
\label{fig:innerlayer}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{figs/InnerLayer/modifiedFlux.pdf}
\caption{Flux imbalance in inner layer solutions}
\label{fig:innerlayer_flux}
\end{figure}

@@

\subsubsection{Hemker Problem}
The Hemker problem is defined on a domain
$\Omega=\{[-3,9]\times[-3,3]\}\setminus\{(x,y):x^2+y^2<1\}$, essentially a simplified
model of flow past an infinite cylinder. We start with the initial mesh shown
in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
fifth order curvilinear polynomial segments. As we refine, the new elements are
fitted to better approximate an exact circle.The boundary conditions are $\hat
t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left inflow boundary,
$\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
cylinder. We run with $\epsilon=10^{-3}$.

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
\caption{Initial mesh for the Hemker problem}
\label{fig:hemkerInitial}
\end{figure}

\begin{figure}[p]
\centering
\centering
\includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
\caption{Flux imbalance in Hemker problem}
\label{fig:hemkerFlux}
\end{figure}

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.6\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/modified8nc.png}
\end{subfigure}
\begin{subfigure}[t]{0.6\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/modified8nc_mesh.png}
\caption{Nonconservative}
\label{fig:hemkerModified8nc}
\end{subfigure}
\begin{subfigure}[t]{0.6\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/modified8c.png}
\end{subfigure}
\begin{subfigure}[t]{0.6\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/modified8c_mesh.png}
\caption{Conservative}
\label{fig:hemkerModified8c}
\end{subfigure}
\caption{Hemker problem after 8 refinements}
\label{fig:hemker8}
\end{figure}

>>>>

% \subsubsection{Skewed Convection-Diffusion Problem}
% This is a standard convection-diffusion problem with a skewed convection
% vector relative to the mesh. We take $\bbeta=(2,1)$, and on the left and
% bottom inflow boundaries we impose $\hat t=1-x-y$ while the right and top
% boundaries have $\hat u=0$. We solve for $\epsilon=10^{-4}$.
%
% \begin{figure}[p]
% \centering
% \begin{subfigure}[t]{0.45\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/Confusion/modified8nc.png}
% \includegraphics[width=\textwidth]{figs/Confusion/modified8nc_mesh.png}
% \caption{Nonconservative}
% \label{fig:confusionModified8nc}
% \end{subfigure}
% \begin{subfigure}[t]{0.45\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/Confusion/modified8c.png}
% \includegraphics[width=\textwidth]{figs/Confusion/modified8c_mesh.png}
% \caption{Conservative}
% \label{fig:confusionModified8c}
% \end{subfigure}
% \caption{Skewed convection-diffusion problem after 8 refinements}
% \label{fig:confusion}
% \end{figure}
%
% \begin{figure}[h!]
% \centering
% \includegraphics[width=0.8\textwidth]{figs/Confusion/modifiedFlux.pdf}
% \caption{Flux imbalance in skewed convection-diffusion solutions}
% \label{fig:confusionFlux}
% \end{figure}
%
% \subsubsection{Double Glazing Problem}
% This nominal problem definition takes the same unit square domain with
% \[
% \bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad
% \hat u=
% \begin{cases}
% 1 & \mbox{on }\Gamma_{right}\\
% 0 & \mbox{else }
% \end{cases}\,,
% \]
% except that this definition for the boundary is not legal for $\hat u\in
% H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
% width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The
% results are for $\epsilon=10^{-2}$.
%
% \begin{figure}[p]
% \centering
% \begin{subfigure}[t]{0.45\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5nc.png}
% \caption{Nonconservative}
% \label{fig:doubleglazingGraph6c}
% \end{subfigure}
% \begin{subfigure}[t]{0.45\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5c.png}
% \caption{Conservative}
% \label{fig:doubleglazingRobust6c}
% \end{subfigure}
% \caption{Double glazing problem after 5 refinements}
% \label{fig:doubleglazing}
% \end{figure}
%
% \begin{figure}[p]
% \centering
% \includegraphics[width=0.8\textwidth]{figs/DoubleGlazing/modifiedFlux.pdf}
% \caption{Flux imbalance in double glazing problem}
% \label{fig:doubleglazingFlux}
% \end{figure}

@@

% \subsubsection{Wedge Problem}
% We devised this problem to examine some of the issues we were having blow up
% of the solution under the robust test norm. The domain is a rectangle
% $[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
% the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
% $\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
% inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
% u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
% of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
% of the wedge.
%
% \begin{figure}[p]
% \centering
% \begin{subfigure}[t]{0.4\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/Wedge/modified16nc.png}
% \includegraphics[width=\textwidth]{figs/Wedge/modified16nc_mesh.png}
% \caption{Nonconservative}
% \label{fig:wedgeGraph16nc}
% \end{subfigure}
% \begin{subfigure}[t]{0.4\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/Wedge/modified16c.png}
% \includegraphics[width=\textwidth]{figs/Wedge/modified16c_mesh.png}
% \caption{Conservative}
% \label{fig:wedgeRobust16nc}
% \end{subfigure}
% \caption{Wedge problem after 16 refinements}
% \label{fig:wedge}
% \end{figure}
%
% \begin{figure}[h!]
% \centering
% \includegraphics[width=0.8\textwidth]{figs/Wedge/modifiedFlux.pdf}
% \caption{Flux imbalance in wedge solutions}
% \label{fig:wedge_flux}
% \end{figure}
%
% \subsubsection{Inner Layer Problem}
% In this problem, $\bbeta=(\frac{\sqrt{3}}{2},\frac{1}{2})^T$ and we have a
% discontinuous flux inflow condition where $\hat t=0$ if $y\le0.2$ and $\hat
% t=\bbeta\cdot\mathbf{n}$ if $y>0.2$. On the outflow, $\hat u=0$. We use a very
% small diffusion scale of $\epsilon=10^{-6}$ which creates a very thin inner
% layer.
% % Nonconservative solution in range $[-0.38, 1.34]$.
% % Conservative solution in range $[-0.39, 1.38]$.
%
% \begin{figure}[p]
% \centering
% \begin{subfigure}[t]{0.45\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc.png}
% \includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc_mesh.png}
% \caption{Nonconservative}
% \label{fig:innerlayer8nc}
% \end{subfigure}
% \begin{subfigure}[t]{0.45\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/InnerLayer/modified8c.png}
% \includegraphics[width=\textwidth]{figs/InnerLayer/modified8c_mesh.png}
% \caption{Conservative}
% \label{fig:innerlayer8c}
% \end{subfigure}
% \caption{Inner layer problem after 8 refinements}
% \label{fig:innerlayer}
% \end{figure}
%
% \begin{figure}[h!]
% \centering
% \includegraphics[width=0.8\textwidth]{figs/InnerLayer/modifiedFlux.pdf}
% \caption{Flux imbalance in inner layer solutions}
% \label{fig:innerlayer_flux}
% \end{figure}

@@

% \subsubsection{Hemker Problem}
% The Hemker problem is defined on a domain
% $\Omega=\{[-3,9]\times[-3,3]\}\setminus\{(x,y):x^2+y^2<1\}$, essentially a simplified
% model of flow past an infinite cylinder. We start with the initial mesh shown
% in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
% fifth order curvilinear polynomial segments. As we refine, the new elements are
% fitted to better approximate an exact circle.The boundary conditions are $\hat
% t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left inflow boundary,
% $\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
% boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
% cylinder. We run with $\epsilon=10^{-3}$.
%
% \begin{figure}[p]
% \centering
% \includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
% \caption{Initial mesh for the Hemker problem}
% \label{fig:hemkerInitial}
% \end{figure}
%
% \begin{figure}[p]
% \centering
% \centering
% \includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
% \caption{Flux imbalance in Hemker problem}
% \label{fig:hemkerFlux}
% \end{figure}
%
% \begin{figure}[p]
% \centering
% \begin{subfigure}[t]{0.6\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/Hemker/modified8nc.png}
% \end{subfigure}
% \begin{subfigure}[t]{0.6\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/Hemker/modified8nc_mesh.png}
% \caption{Nonconservative}
% \label{fig:hemkerModified8nc}
% \end{subfigure}
% \begin{subfigure}[t]{0.6\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/Hemker/modified8c.png}
% \end{subfigure}
% \begin{subfigure}[t]{0.6\textwidth}
% \centering
% \includegraphics[width=\textwidth]{figs/Hemker/modified8c_mesh.png}
% \caption{Conservative}
% \label{fig:hemkerModified8c}
% \end{subfigure}
% \caption{Hemker problem after 8 refinements}
% \label{fig:hemker8}
% \end{figure}
